---
title: "Assignment_B1"
author: "Jacky Yiu"
date: "2023-10-31"
output: github_document
Roxygen: list(markdown = TRUE)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prerequisites

Please install the following libraries

```{r}
library(datateachr)
library(tidyverse)
library(testthat)
library(dplyr)
```

## Exercise 1: Make a Function (25 points)

### Function Description:

During the tidying part of my MDA part 2, I try to tidy 2 columns with comma-separated categorical values and a column with slash-separated categorical values.

First I separate the delimiter-separated categorical values into multiple rows using `separate_rows`.

Then, I adds a new column called `value` with the constant value "TURE."

Next, it pivots the data so that each unique categorical values from the separated column becomes a separate column in the resulting dataset, with "TURE" indicating the presence of that categorical value and "FALSE" as a fill value where the categorical value is absent.

Finally, I prefixes the column names with "column_name\_" to create a tidy dataset where each column represents a specific Value and indicates its presence or absence in each data point.

To handle NA, if the original value is "NA", then "column_name_NA" will be TRUE, and the rest of the newly generated column will be FALSE

the code chunk below is an example, the following operation turn the column `amenities` into 8 different columns containing "TRUE" or "FALSE".

```{r}
apartments_tidy <- apt_buildings %>%
  separate_rows(amenities, sep = " , ") %>% #first separating amenities into multiple rows using separate_rows
  mutate(value = TRUE) %>%  #adds a new column called "value" with the constant value "YES.", meaning the presence of the amenity
  pivot_wider(names_from = amenities, values_from = value, values_fill =list(value = FALSE), names_prefix = "amenities_")
```

### Before

in the original data, the column `amenities` contains comma separated values, which is not tidy

```{r}
glimpse(apt_buildings %>% 
  select(starts_with("amenities"))) 
```

### After

amenities is separated into 8 separated columns, `amenities_NA` is `TURE` when the original data is NA

```{r}
glimpse(apartments_tidy %>% 
  select(starts_with("amenities"))) 
```

I will turn the operation in to a function and name my function `tidy_column_with_delimiter_seperated_values`

I will write the code and the documentation together in the next section, please see the next section .

## Exercise 2: Document your Function (20 points)

```{r}
#' Tidy Column with Delimiter-Separated Values
#'
#' This function separates a column with delimiter-separated values into multiple rows and pivots it to wide format, indicating the presence of each value.
#'
#' @param data A tibble/data frame containing the column to be tidied.
#' @param delimiter The delimiter used to separate values within the column.
#' @param column The name of the column that contains delimiter-separated values.
#'
#' @return A modified tibble/data frame where the specified column has been separated into multiple rows and pivoted to a wider format, showing the presence of each 'value.'
#' 
tidy_column_with_delimiter_seperated_values <- function(data, delimiter, column) {
  col_name <- deparse(substitute(column)) 
  stopifnot(col_name %in% colnames(data))
  stopifnot(is.character(data[[col_name]]))
  
  data %>%
    separate_rows({{ column }}, sep = delimiter) %>% 
    mutate(value = TRUE) %>%
    pivot_wider(names_from = {{ column }}, 
                values_from = value, 
                values_fill =  FALSE, 
                names_prefix = paste0(col_name , "_"))
}

```

## Exercise 3: Include examples (15 points)

### Example 1

Here, we create a different dataframe that use ";" as delimiter, and the column name is "`Facilities`" .

```{r}
example_1 <- data.frame(
  ID = 1:4,
  Facilities = c("Tennis;Spa;Pool", "Gym;Sauna", "Parking;Wifi", "Garden")
)

example_1
```

We see that the function run successfully, it turn facilities in to 8 different columns containing Boolean values

```{r}
tidy_column_with_delimiter_seperated_values(example_1, ";", Facilities)
```

### Example 2

This time, we create a dataset with delimiter-separated values and missing data

```{r}
example_2 <- data.frame(
  ID = 1:4,
  Services = c("Cleaning,Laundry", "Room Service,Pool", NA, "Gym,Spa")
)
example_2
```

The function work as expect, the data point with NA is TRUE in `Services_NA` and FALSE in anywhere else.

```{r}
tidy_column_with_delimiter_seperated_values(example_2, ",", Services)
```

## Exercise 4: Test the Function (25 points)

```{r}

test_that("Testing tidy_column_with_delimiter_seperated_values function", {
  # Test 1: Vector with no NAs
  df_no_na <- data.frame(ID = 1:3, Amenities = c("Wifi,Pool,Gym", "Parking,Wifi", "Gym,Spa"))
  output_no_na <- tidy_column_with_delimiter_seperated_values(df_no_na, ",", Amenities)
  expect_true(all(c("Amenities_Wifi", "Amenities_Pool", "Amenities_Gym") %in% colnames(output_no_na)))
  expect_equal(ncol(output_no_na), 6) 

  # Test 2: Vector that has NAs
  df_with_na <- data.frame(ID = 1:4, Amenities = c("Wifi,Pool,Gym", NA, "Parking,Wifi", "Gym,Spa"))
  output_with_na <- tidy_column_with_delimiter_seperated_values(df_with_na, ",", Amenities)
  expect_true(all(c("Amenities_Wifi", "Amenities_Pool", "Amenities_NA") %in% colnames(output_with_na)))
  expect_identical(nrow(output_with_na), nrow(df_with_na)) 

  # Test 3: Vector of length 0
  df_empty <- data.frame(ID = numeric(0), Amenities = character(0))
  output_empty <- tidy_column_with_delimiter_seperated_values(df_empty, ",", Amenities)
  expect_equal(nrow(output_empty), 0)

  # Test 4: Test for passing a non-existence column to the function, should return Error
  df_nonexistent_column <- data.frame(ID = 1:3, Features = c("Forest,Lake", "Lake,Pool", "Gym,Spa"))
  expect_error(tidy_column_with_delimiter_seperated_values(df_nonexistent_column, ",", Nonexistent_Column))

})
```
